### 2016-05-27 R/ITHIM.Rmd
Almost have AF replicating...

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
```
```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install_github("syounkin/ITHIM")
library("ITHIM")
date()
```

### Instanciation

```{r instantiate}
ITHIM.baseline <- list(
  parameters = parameters <- createParameterList(baseline = TRUE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
ITHIM.scenario <- list(
  parameters = parameters <- createParameterList(baseline = FALSE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)

RR <- createActiveTransportRRs()
RR <- matrix(RR$BreastCancer[,"F"],nrow=nAgeClass,ncol = 5, byrow = FALSE)

totalMETs.baseline <- mapply("+",ITHIM.baseline$quintiles$TotalTravelMET,computeNonTravelMETs(),SIMPLIFY=FALSE)
totalMETs.scenario <- mapply("+",ITHIM.scenario$quintiles$TotalTravelMET,computeNonTravelMETs(),SIMPLIFY=FALSE)

RR^(totalMETs$F^0.5)

```{r ITHIM}
names(ITHIM)
```

For help run the following.
```{r help, eval = FALSE}
help(createParameterList)
help(computeMeansMatrices)
help(getQuintiles)
```

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
```
```{r loadITHIM, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
library("devtools")
install("~/ITHIM/")
# install_github("syounkin/ITHIM", ref = "devel", force = TRUE)
library("ITHIM")
date()
```

### Running in R

```{r instantiate}
ITHIM.baseline <- list(
  parameters = parameters <- createParameterList(baseline = TRUE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
ITHIM.scenario <- list(
  parameters = parameters <- createParameterList(baseline = FALSE),
  means = means <- computeMeanMatrices(parameters),
  quintiles = quintiles <- getQuintiles(means)
)
```
Now we can compute the attributable fraction (AF).

```{r RRs}
RR <- createActiveTransportRRs()
RR.baseline <- lapply(RR, MET2RR, ITHIM.baseline$quintiles$TotalMET)
RR.scenario <- lapply(RR, MET2RR, ITHIM.scenario$quintiles$TotalMET)

diseaseBurden.scenario <- mapply(ratioForList,RR.baseline, RR.scenario, SIMPLIFY = FALSE)
diseaseBurden.baseline <- mapply(ratioForList,RR.baseline, RR.baseline, SIMPLIFY = FALSE) # What!
AF <- mapply(AFForList, diseaseBurden.scenario,diseaseBurden.baseline, SIMPLIFY = FALSE)
```

Note that some of the AF values will disagree with the EXCEL
spreadsheet because Diabetes, HHD_Air, CVD_Air and Stroke_Air do not
combine travel METs with non-travel METs.

```{r AF}
100*round(AF$BreastCancer[-(1:2),],4)

```{r explore}
names(ITHIM.baseline$parameters)
```

We use Rws to estimate mean walking speed and from that mean walking
METs.  Mean cycling METs, however, is constant and is not a function
of mean cycling speed or Rcs.  So, I do not think Rcs is currently
used.

To see the help page for a function use help().
```{r help, eval = FALSE}
help(createParameterList)
help(computeMeansMatrices)
help(getQuintiles)
```
